### 2019-10-20 Code/pole_table.tex
split Greenland into pieces and make Superior/Slave reconstructions

      Laurentia-Superior(East) &                                         SENNETERRE &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Buchan1993a\} \\
      Laurentia-Superior(East) &                                       NIPISSING N1 &      A &     279.0 &      47.0 & 272.0 & -17.0 &      10.0 &     2217\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\

@@

      Laurentia-Superior(East) &                                        BISCOTASING &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\

@@

           Laurentia-Greenland &                        Melville Bugt diabase dykes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\

@@

                     Laurentia &                         Mackenzie dykes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\

@@

                     Laurentia &                             Sudbury Dykes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
            Laurentia-Scotland &                                   MEAN Stoer Group &      B &     354.5 &      58.0 & 238.4 &  37.2 &       7.7 &   1199\$\textasciicircum \{+70\}\$\$\_\{-70\}\$ &                                                NaN \\

@@

                     Laurentia &                                      Abitibi Dykes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                       MEAN Nipigon sills and lavas &      A &     270.9 &      49.1 & 217.8 &  47.2 &       4.0 &     1111\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                                NaN \\
                     Laurentia &                           Lower Osler volcanics -R &      A &     272.3 &      48.8 & 218.6 &  40.9 &       4.8 &     1108\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &             Lowermost Mamainse Point volcanics -R1 &      A &     275.3 &      47.1 & 227.0 &  49.5 &       5.3 &     1108\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                          Middle Osler volcanics -R &      A &     272.4 &      48.8 & 211.3 &  42.7 &       8.2 &     1107\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                                NaN \\
                     Laurentia &                           Upper Osler volcanics -R &      A &     272.4 &      48.7 & 201.6 &  42.5 &       3.7 &     1105\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                 Lower Mamainse Point volcanics -R2 &      A &     275.3 &      47.1 & 205.2 &  37.5 &       4.5 &     1105\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &     Mamainse Point volcanics -C (lower N, upper R) &      A &     275.3 &      47.1 & 189.7 &  36.1 &       4.9 &     1101\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                                NaN \\
                     Laurentia &              Uppermost Mamainse Point volcanics -N &      A &     275.3 &      47.1 & 183.2 &  31.2 &       2.5 &     1098\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                               North Shore lavas -N &      A &     268.7 &      46.3 & 181.3 &  34.5 &       2.8 &     1097\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                              Chengwatana Volcanics &      B &     267.3 &      45.4 & 186.1 &  30.9 &       8.2 &     1095\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                             Portage Lake Volcanics &      A &     271.2 &      47.0 & 178.0 &  26.7 &       4.7 &     1095\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                    Cardenas Basalts and Intrusions &      B &     248.1 &      36.1 & 185.0 &  32.0 &       8.0 &     1091\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
                     Laurentia &                           Schroeder Lutsen Basalts &      A &     269.1 &      47.5 & 187.8 &  27.1 &       3.0 &     1090\$\textasciicircum \{+2\}\$\$\_\{-7\}\$ &                                                NaN \\
                     Laurentia &                        Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                                NaN \\
                     Laurentia &                                   Lake Shore Traps &      A &     271.9 &      47.6 & 186.4 &  23.1 &       4.0 &     1087\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                      Michipicoten Island Formation &      A &     274.3 &      47.7 & 174.7 &  17.0 &       4.4 &     1084\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                                NaN \\
                     Laurentia &                                    Freda Sandstone &      B &     271.5 &      47.0 & 179.0 &   2.2 &       4.2 &   1050\$\textasciicircum \{+30\}\$\$\_\{-30\}\$ &                                                NaN \\
                     Laurentia &                                     Nonesuch Shale &      B &     271.5 &      47.0 & 178.1 &   7.6 &       5.5 &   1050\$\textasciicircum \{+30\}\$\$\_\{-30\}\$ &                                                NaN \\
                     Laurentia &                              Haliburton Intrusions &      B &     281.4 &      45.0 & 141.9 & -32.6 &       6.3 &   1015\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &                                                NaN \\
            Laurentia-Scotland &                                MEAN Torridon Group &      B &     354.3 &      57.9 & 220.9 & -17.7 &       7.1 &  925\$\textasciicircum \{+145\}\$\$\_\{-145\}\$ &                                                NaN \\
            Laurentia-Svalbard &                      Lower Grusdievbreen Formation &      B &      18.0 &      79.0 & 204.9 &  19.6 &      10.9 &    831\$\textasciicircum \{+20\}\$\$\_\{-20\}\$ &                                                NaN \\
            Laurentia-Svalbard &                      Upper Grusdievbreen Formation &      B &      18.2 &      78.9 & 252.6 &  -1.1 &       6.2 &    800\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                                NaN \\
                     Laurentia &                     MEAN Wyoming "Gunbarrel" dykes &      B &     248.7 &      44.8 & 129.4 &  13.9 &       8.2 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                           Tsezotene Sills Combined &      B &     235.0 &      63.5 & 137.8 &   1.6 &       5.0 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                               Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &    775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                                NaN \\
            Laurentia-Svalbard &                          Svanbergfjellet Formation &      B &      18.0 &      78.5 & 226.8 &  25.9 &       5.8 &    760\$\textasciicircum \{+30\}\$\$\_\{-30\}\$ &                                                NaN \\
                     Laurentia &                          Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                                   Long Range Dykes &      B &     303.3 &      53.7 & 355.3 &  19.0 &      17.4 &      615\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 321.5 & -34.2 &      15.4 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 332.7 &  42.6 &      12.0 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
                     Laurentia &                         Callander Alkaline Complex &      B &     280.6 &      46.2 & 301.4 &  46.3 &       6.0 &      575\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
                     Laurentia &                                   Catoctin Basalts &      B &     281.8 &      38.5 & 296.7 &  42.0 &      17.5 &      572\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
                     Laurentia &                        Sept-Iles Layered Intrusion &      B &     293.5 &      50.2 & 321.0 & -20.0 &       6.7 &      565\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                                NaN \\

>>>>

      Laurentia-Superior(East) &                                         Senneterre &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Buchan1993a\} \\
      Laurentia-Superior(East) &                                       Nipissing N1 &      A &     279.0 &      47.0 & 272.0 & -17.0 &      10.0 &     2217\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\

@@

      Laurentia-Superior(East) &                                        Biscotasing &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\

@@

           Laurentia-Greenland &                        Melville Bugt diabase dykes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Halls2011a\} \\

@@

                     Laurentia &                         Mackenzie dykes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\

@@

                     Laurentia &                             Sudbury Dykes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Palmer1977a\} \\
            Laurentia-Scotland &                                   MEAN Stoer Group &      B &     354.5 &      58.0 & 238.4 &  37.2 &       7.7 &   1199\$\textasciicircum \{+70\}\$\$\_\{-70\}\$ &                  Lulea Nordic workshop calculation \\

@@

                     Laurentia &                                      Abitibi Dykes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Ernst1993a\} \\
                     Laurentia &                       MEAN Nipigon sills and lavas &      A &     270.9 &      49.1 & 217.8 &  47.2 &       4.0 &     1109\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                  Lulea Nordic workshop calculation \\
                     Laurentia &             Lowermost Mamainse Point volcanics -R1 &      A &     275.3 &      47.1 & 227.0 &  49.5 &       5.3 &     1109\$\textasciicircum \{+2\}\$\$\_\{-3\}\$ &                         \textbackslash cite\{Swanson-Hysell2014a\} \\
                     Laurentia &                           Lower Osler volcanics -R &      A &     272.3 &      48.8 & 218.6 &  40.9 &       4.8 &     1108\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                         \textbackslash cite\{Swanson-Hysell2014b\} \\
                     Laurentia &                          Middle Osler volcanics -R &      A &     272.4 &      48.8 & 211.3 &  42.7 &       8.2 &     1107\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                         \textbackslash cite\{Swanson-Hysell2014b\} \\
                     Laurentia &                           Upper Osler volcanics -R &      A &     272.4 &      48.7 & 203.4 &  42.3 &       3.7 &     1105\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                         \textbackslash cite\{Swanson-Hysell2019a\} \\
                     Laurentia &                 Lower Mamainse Point volcanics -R2 &      A &     275.3 &      47.1 & 205.2 &  37.5 &       4.5 &     1105\$\textasciicircum \{+3\}\$\$\_\{-4\}\$ &                         \textbackslash cite\{Swanson-Hysell2014a\} \\
                     Laurentia &     Mamainse Point volcanics -C (lower N, upper R) &      A &     275.3 &      47.1 & 189.7 &  36.1 &       4.9 &     1101\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                         \textbackslash cite\{Swanson-Hysell2014a\} \\
                     Laurentia &                               North Shore lavas -N &      A &     268.7 &      46.3 & 181.7 &  31.1 &       2.1 &     1097\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &              \textbackslash cite\{Tauxe2009a,Swanson-Hysell2019a\} \\
                     Laurentia &                              Chengwatana Volcanics &      B &     267.3 &      45.4 & 186.1 &  30.9 &       8.2 &     1095\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash citep\{Kean1997a\} \\
                     Laurentia &                             Portage Lake Volcanics &      A &     271.2 &      47.0 & 182.5 &  27.5 &       2.3 &     1095\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &  \textbackslash cite\{Books1972a, Hnat2006a\} as calculated in ... \\
                     Laurentia &              Uppermost Mamainse Point volcanics -N &      A &     275.3 &      47.1 & 183.2 &  31.2 &       2.5 &     1094\$\textasciicircum \{+6\}\$\$\_\{-4\}\$ &                         \textbackslash cite\{Swanson-Hysell2014a\} \\
                     Laurentia &                    Cardenas Basalts and Intrusions &      B &     248.1 &      36.1 & 185.0 &  32.0 &       8.0 &     1091\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                   \textbackslash cite\{Weil2003a\} \\
                     Laurentia &                           Schroeder Lutsen Basalts &      A &     269.1 &      47.5 & 187.8 &  27.1 &       3.0 &     1090\$\textasciicircum \{+2\}\$\$\_\{-7\}\$ &                              \textbackslash cite\{Fairchild2017a\} \\
                     Laurentia &                        Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                               \textbackslash cite\{Donadini2011a\} \\
                     Laurentia &                                   Lake Shore Traps &      A &     271.9 &      47.6 & 186.4 &  23.1 &       4.0 &     1086\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                                NaN \\
                     Laurentia &                      Michipicoten Island Formation &      A &     274.3 &      47.7 & 174.7 &  17.0 &       4.4 &     1084\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                              \textbackslash cite\{Fairchild2017a\} \\
                     Laurentia &                                     Nonesuch Shale &      B &     271.5 &      47.0 & 178.1 &   7.6 &       5.5 &    1080\$\textasciicircum \{+4\}\$\$\_\{-10\}\$ &                                  \textbackslash cite\{Henry1977a\} \\
                     Laurentia &                                    Freda Sandstone &      B &     271.5 &      47.0 & 179.0 &   2.2 &       4.2 &   1070\$\textasciicircum \{+14\}\$\$\_\{-10\}\$ &                                  \textbackslash cite\{Henry1977a\} \\
                     Laurentia &                              Haliburton Intrusions &      B &     281.4 &      45.0 & 141.9 & -32.6 &       6.3 &   1015\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &                                \textbackslash cite\{Warnock2000a\} \\
            Laurentia-Scotland &                                MEAN Torridon Group &      B &     354.3 &      57.9 & 220.9 & -17.7 &       7.1 &  925\$\textasciicircum \{+145\}\$\$\_\{-145\}\$ &                  Lulea Nordic workshop calculation \\
            Laurentia-Svalbard &                      Lower Grusdievbreen Formation &      B &      18.0 &      79.0 & 204.9 &  19.6 &      10.9 &    831\$\textasciicircum \{+20\}\$\$\_\{-20\}\$ &                                 \textbackslash cite\{Maloof2006a\} \\
            Laurentia-Svalbard &                      Upper Grusdievbreen Formation &      B &      18.2 &      78.9 & 252.6 &  -1.1 &       6.2 &    800\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                 \textbackslash cite\{Maloof2006a\} \\
                     Laurentia &                     MEAN Wyoming "Gunbarrel" dykes &      B &     248.7 &      44.8 & 129.4 &  13.9 &       8.2 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &  Lulea Nordic workshop calculation based on dat... \\
                     Laurentia &                           Tsezotene Sills Combined &      B &     235.0 &      63.5 & 137.8 &   1.6 &       5.0 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                   \textbackslash cite\{Park1989a\} \\
                     Laurentia &                               Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &    775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                   \textbackslash cite\{Weil2006a\} \\
            Laurentia-Svalbard &                          Svanbergfjellet Formation &      B &      18.0 &      78.5 & 226.8 &  25.9 &       5.8 &    760\$\textasciicircum \{+30\}\$\$\_\{-30\}\$ &                                 \textbackslash cite\{Maloof2006a\} \\
                     Laurentia &                          Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                               \textbackslash cite\{Denyszyn2009a\} \\
                     Laurentia &                                   Long Range Dykes &      B &     303.3 &      53.7 & 355.3 &  19.0 &      17.4 &      615\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Murthy1992a\} \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 321.5 & -34.2 &      15.4 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 332.7 &  42.6 &      12.0 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                         Callander Alkaline Complex &      B &     280.6 &      46.2 & 301.4 &  46.3 &       6.0 &      575\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Symons1991a\} \\
                     Laurentia &                                   Catoctin Basalts &      B &     281.8 &      38.5 & 296.7 &  42.0 &      17.5 &      572\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Meert1994a\} \\
                     Laurentia &                        Sept-Iles Layered Intrusion &      B &     293.5 &      50.2 & 321.0 & -20.0 &       6.7 &      565\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                 \textbackslash cite\{Tancyk1987a\} \\
